Verifying Demonstrations

### 2018-10-31 paper/privacy-properties.tex
now it compiles; added framing for pseudonym reuse

As a consequence, this leaves us with with what would correspond to vote privacy.
In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.

We can thus summarize the desired privacy properties as follows:
\begin{requirements}[P]
\item\label{ProofUnlink} \emph{Proof Unlinkability (Anonymity)}: every
  participant's real (long-term) 
  identity (\(P\)) must be unlinkable to their participation proofs $\prf_{\pid, \prtst}$
\item\label{ProtestUnlink} \emph{Protest Unlinkability}: protesters'
  participation proofs $\prf_{\pid, \prtst}$ must be 
  unlinkable between protests ($\cid, \cid'$)
\item\label{WitnessUnlink}\emph{Witness Unlinkability}:  witnesses'
  participation proof shares $\(\psh = (\cid, t, l, \pid, \wid)\)$ must be unlinkable between 
  protesters. ($\pid, \pid'$)
\end{requirements}

>>>>

As a consequence, this leaves us with with what would correspond to vote privacy.
In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.
Moreover, any temporary identifiers such as pseudonyms may only be
reused when strictly necessary for the fulfillment of verifiability
properties listed in \label{verifiability-properties} to prevent
inference on long-term identities by repeated samples and side information.

We can thus summarize the desired privacy properties as follows:
\begin{requirements}[P]
\item\label{ProofUnlink} \emph{Proof Unlinkability (Anonymity)}: every
  participant's real (long-term) 
  identity (\(P\)) must be unlinkable to their participation proofs \(\prf_{\pid, \prtst}\)
\item\label{ProtestUnlink} \emph{Protest Unlinkability}: protesters'
  participation proofs \(\prf_{\pid, \prtst}\) must be 
  unlinkable between protests (\(\cid, \cid' \))
\item\label{WitnessUnlink}\emph{Witness Unlinkability}:  witnesses'
  participation proof shares \(\psh = (\cid, t, l, \pid,\wid)\) 
must be unlinkable between 
  protesters. (\(\pid, \pid' \))
\end{requirements}
